%-------------------------
% Resume in LateX
% Author : Jaewoo Jung
% License : MIT
% Reference : https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\listItem}[1]{
  \item\small{
  {#1 \vspace{-2pt}}
  }
}

\newcommand{\highlightSubheading}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        #1 & #2 \\
        \multicolumn{2}{p{0.97\textwidth}}{\small #3}%
    \end{tabular*}\vspace{-5pt}
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      {\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\newcommand{\email}{dev@lukael.kr}
\newcommand{\home}{https://lukael.kr}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{\home}{\Large Jaewoo Jung}} & Email: \href{mailto:\email}{\email}\\
  \href{\home}{\home} & \textit{Updated: \today} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Yonsei University}{Seoul, Korea}
      {Ph.D Candidate in Electrical and Electronics Engineering}
      {2020 -- Present}
    \resumeSubheading
      {Yonsei University}{Seoul, Korea}
      {B.S. in Electrical and Electronics Engineering}
      {2015 -- 2020}
    \resumeSubheading
      {Changwon Science High School}{Changwon, Korea}
      {Chemistry, Early graduation}
      {2013 -- 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Seoul National University}{Seoul, Korea}
      {Research Engineer, Imaging Intelligence Laboratory (Prof. Seung Ah Lee)}{July 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Lensless Imaging}
          {: deep learning for image reconstruction, model based deep learning network}
      \resumeItemListEnd

    \resumeSubheading
      {LUXROBO Ltd.}{Seoul, Korea}
      {Research Engineer}{Aug 2023 -- June 2025}
      \resumeItemListStart
        \resumeItem{MODI Factory}
          {: Electronic Design Automation, Golang Backend, MySQL database, Reinforcement Learning, MLOps}
      \resumeItemListEnd
      
    \resumeSubheading
      {Yonsei University}{Seoul, Korea}
      {Graduate Research Assistant, Optical Imaging Systems Laboratory (Prof. Seung Ah Lee)}{Mar 2020 -- Aug 2023}
      \resumeItemListStart
        \resumeItem{Lensless Microscopy}
          {: digital in-line holography}
        \resumeItem{Lensless Imaging}
          {: deep learning for image reconstruction, model based deep learning network}
      \resumeItemListEnd
    
    \resumeSubSubheading
      {Internship, Optical Imaging Systems Laboratory (Prof. Seung Ah Lee)}{Jan 2019 -- Feb 2020}
      \resumeItemListStart
        \resumeItem{Human-Biology Interaction}
          {: biotic games}
        \resumeItem{Lensless Microscopy}
          {: digital in-line holography}
    
    \resumeItemListEnd

    \resumeSubheading
      {Toky}{Seoul, Korea}
      {Co-Founder, Engineer}{Jul 2019 -- Feb 2020}
      \resumeItemListStart
        \resumeItem{Voice recognition kiosk}
          {: voice recognition, embedded software}
      \resumeItemListEnd

    \resumeSubheading
      {Yonsei University}{Seoul, Korea}
      {Internship, Biological Cybernetics Laboratory (Prof. Dae Eun Kim)}{Aug 2016 -- Dec 2018}
      \resumeItemListStart
        \resumeItem{Swarm robotics}
          {: Hardware, FreeRTOS, Wi-Fi, Bluetooth, Vibration control, Software, Formation, charging system}
      \resumeItemListEnd

    \resumeSubheading
      {LUXROBO Ltd.}{Seoul, Korea}
      {Research Engineer}{Mar 2017 -- Dec 2017}
      \resumeItemListStart
        \resumeItem{Network Module Firmware(ESP32)}
          {: FreeRTOS, Wi-Fi, BLE, USART}
        \resumeItem{OS Development}
          {: RTOS research, Contiki OS}
        \resumeItem{Bluetooth 5}
          {: Nordic nRF52DK, Mesh Network}
        \resumeItem{NLP}
          {: Chatscript, Slack-Chatscript Linkage(Python)}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

% --------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Programming Skills}{: C/C++, Python, MATLAB, Go}
   }
   \vspace{-5pt}
   
   \item{
     \textbf{Technologies}{: SketchUp, EasyEDA, Git}
   }
   \vspace{-5pt}
   
   \item{
     \textbf{Languages}{: Korean (Native), English (Fluent)}
   }
 \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\section{Publications}
  \resumeSubHeadingListStart
        \listItem{Y. Lee, S. Byun, C. Yi, \textbf{J. Jung} and S. A. Lee, "Rolling shutter speckle plethysmography for quantitative cardiovascular monitoring." Biomedical Optics Express, 15(3), 1540-1552, 2024.}
        \listItem{K. Lee, K. C. Lee, \textbf{J. Jung}, H. Chae, and S. A. Lee, “High-resolution display screen as programmable illumination for Fourier ptychography.” Optics and Lasers in Engineering, 177, 108121, 2024.}
        \listItem{K. C. Lee, J. Bae, N. Baek, \textbf{J. Jung}, W. Park, and S. A. Lee, “Design and single-shot fabrication of lensless cameras with arbitrary point spread functions,” Optica, vol. 10, no. 1, pp. 72–80, 2023.}
        \listItem{C. Yi, \textbf{J. Jung}, J. Im, K. C. Lee, E. Chung, and S. A. Lee, “Single-shot temporal speckle correlation imaging using rolling shutter image sensors,” Optica, vol. 9, no. 11, pp. 1227–1237, 2022.}
        \listItem{N. Baek, Y. Lee, T. Kim, \textbf{J. Jung}, and S. A. Lee, “Lensless polarization camera for single-shot full-stokes imaging,” APL Photonics, 2022.}
        \listItem{Y. Lee, H. Chae, K. C. Lee, N. Baek, T. Kim, \textbf{J. Jung}, and S. A. Lee, “Fabrication of integrated lensless cameras via uv-imprint lithography,” IEEE Photonics Journal, vol. 14, no. 2, pp. 1–8, 2022.}
        \listItem{K. C. Lee, K. Lee, \textbf{J. Jung}, S. H. Lee, D. Kim, and S. A. Lee, “A smartphone based fourier ptychographic microscope using the display screen for illumination,” ACS Photonics, vol. 8, no. 5, pp. 1307–1315, 202}
  \resumeSubHeadingListEnd

%-----------CONFERENCE-----------------
\section{Conference Presentations (Selected)}
  \resumeSubHeadingListStart
    \highlightSubheading
      {Poster, Advanced Biophotonics Conference, SPIE}{2025}
      {\textbf{Jaewoo Jung}, Donggeon Bae, Kyung Chul Lee, Seung Ah Lee, \textit{Multi-view Lensless Imaging using 3D Gaussian Splatting}}
    
    \highlightSubheading
      {Poster, ICEIC, IEEE/IEIE}{2023}
      {\textbf{Jaewoo Jung}, Yujin Lee, Seung Ah Lee, \textit{Jointly Optimized Lensless Imaging System with Trainable Phase Mask for Task-specific Imaging}}
    
    \highlightSubheading
      {Poster, Advanced Biophotonics Conference, OSK}{2022}
      {\textbf{Jaewoo Jung}, Yujin Lee, Seung Ah Lee, \textit{Jointly Optimized Lensless Imaging System with Trainable Phase Mask for Task-specific Imaging}}
    
    \highlightSubheading
      {Oral, IEEE Region 10 Conference, IEEE/IEIE}{2022}
      {\textbf{Jaewoo Jung}, Yujin Lee, Seung Ah Lee, \textit{Jointly Optimized Lensless Imaging System with Trainable Phase Mask for Task-specific Imaging}}
    
    \highlightSubheading
      {Oral, 30th ACM International Conference on Multimedia, ACMMM}{2022}
      {Kyungwon Lee, Yu-Kyung Jang, \textbf{Jaewoo Jung}, Dong Hwan Kim, Hyun Jean Lee, Seung Ah Lee, \textit{EuglPollock: Rethinking Interspecies Collaboration through Art Making}}
    
    \highlightSubheading
      {Poster, Gorden Research Conference Image Science, GRC}{2022}
      {\textbf{Jaewoo Jung}, Donggeon Bae, Kyung Chul Lee, Nakkyu Baek, Tae Young Kim, Ernest K. Ryu, Seung Ah Lee\textit{Deep Learning Approaches for Image Reconstruction in Lensless Cameras}}
    
    \highlightSubheading
      {Oral, ICCE-ASIA, IEEE/IEIE}{2021}
      {\textbf{Jaewoo Jung}, Tae Young Kim, Donggeon Bae, Ernest K. Ryu, Seung Ah Lee, \textit{Image Reconstruction in Lensless Cameras with Unrolled Optimization Algorithms}}
    
    \highlightSubheading
      {Poster, Optics and Photonics Congress, OSK}{2021}
      {\textbf{Jaewoo Jung}, Tae Young Kim, Donggeun Bae, Ernest K. Ryu, Seung Ah Lee, \textit{Unrolled ADMM for Image Reconstruction in Lensless Cameras}}
    
    \highlightSubheading
      {Extended Abstracts(Demo), ACM Conference on Human Factors in Computing Systems, CHI}{2020}
      {Kyungwon Lee, \textbf{Jaewoo Jung}, Seung Ah Lee, \textit{MicroAquarium: An immersive and interactive installation with living microorganisms}}
    
    \highlightSubheading
      {Oral, ICROS, ICROS}{2018}
      {Minchul Kim, \textbf{Jaewoo Jung}, DaeEun Kim, \textit{Swarm Robots Using Vibration Motor Control}}
  
  \resumeSubHeadingListEnd

%-----------PATENT-----------------
\section{Patents}
  \resumeSubHeadingListStart
        \listItem{S. A. Lee, T. Kim, K. Lee, \textbf{J. Jung}, N. Baek, Apparatus and method for measuring eye movement, US Patent, 12062190}
        
        \listItem{S. A. Lee, K. C. Lee, K. Lee, \textbf{J. Jung}, S. H. Lee, Smartphone for obtaining Fourier ptychography image and method for obtaining Fourier ptychography image using smartphone, US Patent, 11880965}
        
        \listItem{S. A. Lee, H. Chae, Y. Lee, K. C. Lee, N. Baek, T. Kim, \textbf{J. Jung}, Methods for manufacturing phase masks and lens-less camera module, US Patent, 12108134}
        
        \listItem{S. A. Lee, K. C. Lee, N. Baek, W. Park, J.H. Bae, \textbf{J. Jung}, Apparatus and method for manufacturing phase masks for lens-less camera, US Patent, 12343954}
  \resumeSubHeadingListEnd

%-----------AWARDS and HONORS-----------------
\section{Awards and Honors}
\resumeSubHeadingListStart
    \highlightSubheading
      {\textbf{Best Poster Awards}, SPIE Advanced Biophotonics Conference}{2025}
      {\textbf{Jaewoo Jung}, Donggeon Bae, Kyung Chul Lee, Seung Ah Lee, \textit{Multi-view Lensless Imaging using 3D Gaussian Splatting}}

    \highlightSubheading
      {\textbf{Best Poster Awards}, Advanced Biophotonics Conference Optical Society of Korea}{2022}
      {\textbf{Jaewoo Jung}, Yujin Lee, Seung Ah Lee, \textit{Jointly Optimized Lensless Imaging System with Trainable Phase Mask for Task-specific Imaging}}

    \highlightSubheading
      {\textbf{Silver Awards}, 28th Samsung Humantech Paper Awards}{2022}
      {Kyung Chul Lee, Nakkyu Baek, \textbf{Jaewoo Jung}, Junghyun Bae, Seung Ah Lee, Wook Park, \textit{Design and Fabrication of Custom Phase-Masks for UltraThin Lensless Camera}}
      
    \highlightSubheading
          {\textbf{Grants}, Undergraduate Research Program, KOFAC}{2019}
          {\textbf{Jaewoo Jung}, Nakkyu Baek, Tae Young Kim, Minhyuk Lee, Seung Ah Lee, \textit{High speed lensless camera for microsaccades measurement}}
          
    \highlightSubheading
          {\textbf{4th Awards}, International Student Car Competition, KTSA}{2019}
          {Vision Team, \textit{Autonomous driving cart}}

    \highlightSubheading
          {\textbf{2nd Awards}, International Student Car Competition, KTSA}{2018}
          {LIDAR Team, \textit{Autonomous driving cart}}

    \highlightSubheading
          {\textbf{1st Awards}, Embedded Software Contest, KESSIA}{2013}
          {Hardware Engineer, \textit{Minesweeper Robot using LEGO Mindstorm}}
    
    \highlightSubheading
          {\textbf{1st Awards}, R\&E Festival, KOSAF}{2013}
          {\textit{Develop Filters made from ESM’s Toxic substances Absorptive Ability}}

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Arxiv Monitoring Bot}
      {}
      
    \resumeSubItem{Dev Environment}
      {}
    
    \resumeSubItem{Various Swarm Behavior Inspired by Nature using Vibration Locomotion Robots}
      {}
    
    \resumeSubItem{Core-XY Autonomous Chess Board}
      {}
    
    \resumeSubItem{Localization using Multiple Gyroscope}
      {}

    \resumeSubItem{Autonomous Driving Model Car}
      {}
    
    \resumeSubItem{Humanoid(KHR-1)}
      {}

    \resumeSubItem{LED cube(8×8×8)}
      {}
      
    \resumeSubItem{Robot Soccer}
      {}
      
    \resumeSubItem{Unmanned Aerial Vehicle (Quadcopter)}
      {}
      
    \resumeSubItem{Guitar Effect Pedal}
      {}
      
  \resumeSubHeadingListEnd

%-----------Teaching and Services-----------------
\section{Teaching and Services}
  \resumeSubHeadingListStart
    \resumeSubItem{Introduction To Bioengineering For EE}
      {(Spring 2023), teaching assistant with Prof. Seung Ah Lee}
    
    \resumeSubItem{Introduction To Bioengineering For EE}
      {(Spring 2021), teaching assistant with Prof. Seung Ah Lee}
    
    \resumeSubItem{Analog Electronics Lab.}
      {(Fall 2020), teaching assistant with Prof. Seung Ah Lee}
  \resumeSubHeadingListEnd

%-----------Extracurricular Experiment-----------------
\section{Extracurricular Experiments}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SBTM(Robot club in Yonsei University)}{Seoul, Korea}
      {President}{Jan 2017 -- Dec 2017}
      \resumeItemListStart
        \resumeItem{}
          {}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-------------------------------------------
\end{document}